Data_visualization

### 2018-08-06 Rmd/Data_visualization.Rmd
changes

pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

#Colur per family

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

@@

soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SELF"] <- "Self"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CONTROL"] <- "Control"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

#changing non_focal species name
ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

>>>>

pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
pein_seed_set_brassicaceae <- filter(pein_seed_set_final, Family %in% c("Brassicaceae"))
pein_seed_set_convolvulaceae <- filter(pein_seed_set_final, Family %in% c("Convolvulaceae"))
pein_seed_set_solanaceae <- filter(pein_seed_set_final, Family %in% c("Solanaceae"))
pein_seed_set_final$Family[is.na(pein_seed_set_final$Family)] <- "Solanum lycopersicum"
pein_seed_set_cross=pein_seed_set_cross[,-c(5,6)]
pein_seed_set_cross$Family <- "other"
pein_seed_set_self=pein_seed_set_self[,-c(5,6)]
pein_seed_set_self$Family <- "other"
pein_seed_set_control=pein_seed_set_control[,-c(5,6)]
pein_seed_set_control$Family <- "other"
pein_seed_set_flower=pein_seed_set_flower[,-c(5,6)]
pein_seed_set_flower$Family <- "other"

pein_seed_set_final=rbind(pein_seed_set_brassicaceae, pein_seed_set_convolvulaceae, 
                          pein_seed_set_solanaceae, pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
                          pein_seed_set_flower)

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

caan_seed_set_brassicaceae <- filter(caan_seed_set_final, Family %in% c("Brassicaceae"))
caan_seed_set_convolvulaceae <- filter(caan_seed_set_final, Family %in% c("Convolvulaceae"))
caan_seed_set_solanaceae <- filter(caan_seed_set_final, Family %in% c("Solanaceae"))
caan_seed_set_final$Family[is.na(caan_seed_set_final$Family)] <- "Solanum lycopersicum"
caan_seed_set_cross=caan_seed_set_cross[,-c(5,6)]
caan_seed_set_cross$Family <- "other"
caan_seed_set_self=caan_seed_set_self[,-c(5,6)]
caan_seed_set_self$Family <- "other"
caan_seed_set_control=caan_seed_set_control[,-c(5,6)]
caan_seed_set_control$Family <- "other"
caan_seed_set_flower=caan_seed_set_flower[,-c(5,6)]
caan_seed_set_flower$Family <- "other"

caan_seed_set_final=rbind(caan_seed_set_brassicaceae, caan_seed_set_convolvulaceae, 
                          caan_seed_set_solanaceae, caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
                          caan_seed_set_flower)

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Because I want to give it specifically order I do it separately
#caan_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

@@

soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

soly_seed_set_brassicaceae <- filter(soly_seed_set_final, Family %in% c("Brassicaceae"))
soly_seed_set_convolvulaceae <- filter(soly_seed_set_final, Family %in% c("Convolvulaceae"))
soly_seed_set_solanaceae <- filter(soly_seed_set_final, Family %in% c("Solanaceae"))
soly_seed_set_final$Family[is.na(soly_seed_set_final$Family)] <- "Solanum lycopersicum"
soly_seed_set_cross=soly_seed_set_cross[,-c(5,6)]
soly_seed_set_cross$Family <- "other"
soly_seed_set_self=soly_seed_set_self[,-c(5,6)]
soly_seed_set_self$Family <- "other"
soly_seed_set_control=soly_seed_set_control[,-c(5,6)]
soly_seed_set_control$Family <- "other"
soly_seed_set_flower=soly_seed_set_flower[,-c(5,6)]
soly_seed_set_flower$Family <- "other"

soly_seed_set_final=rbind(soly_seed_set_brassicaceae, soly_seed_set_convolvulaceae, 
                          soly_seed_set_solanaceae, soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
                          soly_seed_set_flower)
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SELF"] <- "Self"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CONTROL"] <- "Control"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

some_seed_set_brassicaceae <- filter(some_seed_set_final, Family %in% c("Brassicaceae"))
some_seed_set_convolvulaceae <- filter(some_seed_set_final, Family %in% c("Convolvulaceae"))
some_seed_set_solanaceae <- filter(some_seed_set_final, Family %in% c("Solanaceae"))
some_seed_set_final$Family[is.na(some_seed_set_final$Family)] <- "Solanum lycopersicum"
some_seed_set_cross=some_seed_set_cross[,-c(5,6)]
some_seed_set_cross$Family <- "other"
some_seed_set_self=some_seed_set_self[,-c(5,6)]
some_seed_set_self$Family <- "other"
some_seed_set_control=some_seed_set_control[,-c(5,6)]
some_seed_set_control$Family <- "other"
some_seed_set_flower=some_seed_set_flower[,-c(5,6)]
some_seed_set_flower$Family <- "other"

some_seed_set_final=rbind(some_seed_set_brassicaceae, some_seed_set_convolvulaceae, 
                          some_seed_set_solanaceae, some_seed_set_cross, some_seed_set_self, some_seed_set_control,
                          some_seed_set_flower)
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#changing non_focal species name
ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
